% Created 2017-04-17 Mon 18:11
% Intended LaTeX compiler: xelatex
\documentclass[a4paper, notitlepage]{report}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\include{settings/preamble}
\author{Brian McNestry}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Brian McNestry},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 24.5.1 (Org mode 9.0.5)}, 
 pdflang={English}}
\begin{document}

\inserttitlepage

\pagenumbering{roman}

\declaration

\permissiontolend

\insertabstract

\acknowledgements

\tableofcontents

\newpage


\pagenumbering{arabic}

\part{Abstract}
\label{sec:org40b0344}

\part{Introduction}
\label{sec:org993cc07}


\part{Background}
\label{sec:org2b08cc9}
\chapter{Decentralised Grid}
\label{sec:org4c26c2c}
At present in Ireland and in many other countries, the national electric grid
infrastructure is controlled by a central body, namely the ESB. While there are
several electricity providers in Ireland, such as Bord Gáis Energy, SSE
Airtricity and Energy Ireland, each of them use the same distribution network as
one another. Essentially the power is provided from each of the different
providers and then routed into the same centralised hub belonging to the ESB.
From there, each consumer (a household) receives the energy that they pay for
accordingly at a fixed rate through that same infrastructure belonging to the
ESB. This is much the same system as any other country, where there is a
centralised grid. 

This system has been in place for decades and lends itself very well to the
situation where large companies can provide a steady supply of energy by way of
electricity plants that use both renewable and non-renewable energy sources.
Non-renewable energy sources, also known as fossil fuels, include resources such
as coal, gas and oil. While these are finite resources, at present they can be
burned at a steady rate in order to meet the demands of customers. Electricity
from renewable sources can also be produced at a fairly steady rate by placing
large farms in areas that are particularly well suited to the type of renewable
energy being produced. For example, large wind farms are set up in windy
regions far removed from residential or urban areas and solar panels can be
placed in regions that typically enjoy clearer skies than other areas.

However in the future, perhaps the very near future, with the ongoing depletion
of non-renewable resources, more and more people will turn to deploying solar
panels and local wind farms in their locale, regardless of whether or not they
are living in a particularly sunny or windy area.     
\chapter{Smart Grid}
\label{sec:org1094421}

\section{Nanogrids}
\label{sec:org9e07ad8}

\chapter{REFIT Scheme}
\label{sec:org1c01036}
\chapter{Auctions}
\label{sec:org27cdc33}


\chapter{Game Theory}
\label{sec:org45a398e}
\section{Cooperative Game Theory}
\label{sec:org80a932f}

\section{Non-Cooperative Game Theory}
\label{sec:org88a2d30}

\section{Cournot and Stackelberg Games}
\label{sec:org75e5f69}

\chapter{Optimisation Techniques}
\label{sec:orgb090d24}

\section{Convex Optimisation}
\label{sec:org6eb6923}

\section{Hyperplane Projection}
\label{sec:org2528aa4}

\part{Implementation}
\label{sec:orgf9f2f1e}

\chapter{Design}
\label{sec:orga7d36e1}

\chapter{Framework}
\label{sec:org0274879}

\chapter{Processes}
\label{sec:org56faaed}

\part{Conclusion}
\label{sec:org70d817a}

\chapter{Assessment}
\label{sec:orgc5a67ae}

\chapter{Future Work and Continuations}
\label{sec:org1282ad3}

\bibliography{bibliography}
\appendix
\end{document}